---
title: "R Teaching - Coding skill training"
author: "Ralf Becker"
date: "31 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Project

We are using a dataset which is also used in [CORE ECON's Doing Economics projects - Project 3](https://www.core-econ.org/doing-economics/book/text/03-01.html).

It refers to a tax experiment undertaken in the US, where in a restricted area an additional tax was imposed on sugary drinks. Details of the project are available from teh above link.

The results of the experiment are written up in [Silver et al (2017)] (https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1002283). The data are available from the [Global Food Research Program](http://globalfoodresearchprogram.web.unc.edu/research-in-the-united-states/u-s-policy-evaluations/berkeley-ssb-tax/) but here we will use a prepared dataset.

## The Data-Set

Here is the dataset.

```{r}
# loads dat_c (datafile) and var_info
load("SugarTaxData.RData") 
str(dat_c)
```

This uploads two datasets: `dat_c` with the data and `var_info`, the former with the data and the latter with some variable descriptions.

## This is where you get started

...