---
title: "R Teaching - Coding skill training"
author: "Ralf Becker"
date: "31 October 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Project

We are using a dataset which is also used in [CORE ECON's Doing Economics projects - Project 3](https://www.core-econ.org/doing-economics/book/text/03-01.html).

It refers to a tax experiment undertaken in the US, where in a restricted area an additional tax was imposed on sugary drinks. Details of the project are available from teh above link.

The results of the experiment are written up in [Silver et al (2017)] (https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1002283). The data are available from the [Global Food Research Program](http://globalfoodresearchprogram.web.unc.edu/research-in-the-united-states/u-s-policy-evaluations/berkeley-ssb-tax/) but here we will use a prepared dataset.

## The Data-Set

Here is the dataset.

```{r}
# loads dat_c (datafile) and var_info
load("SugarTaxData.RData") 
str(dat_c)
```

This uploads two datasets: `dat_c` with the data and `var_info`, the former with the data and the latter with some variable descriptions.


## How to Google effectively for help

The following is a suggestion for how to demonstrate general error message Googling.

First, student should write a line at a time into a console, testing what they just wrote worked. For example

```{r}
# loads dat_c (datafile) and var_info
load("SugarTaxDat.RData") 
```

The above produces an error message. Students should read the last thing they did. Hopefully this would show them they misspelt `SugarTaxData.RData`.

If this doesn't fix the problem, the student should read the error - checking whether they recognise it, or if it shows they made a typo.

We'll move on to a new error - because the last one was a typo, which Googling often can't fix.

The new error is below

```{r}
# loads dat_c (datafile) and var_info
load("SugarTaxDat.RData")
ggplot(data=dat_c, aes(size, price)) + geom_point()
```

```
Error in ggplot(data = dat_c, aes(size, price)): could not find function "ggplot"
Traceback:
```

With this error, the next step after the above would be to Google the whole thing. Students should check the search results to see if they can resolve the problem. Remind them that they shouldn't be concerned if most of all of the results don't solve their problem, or if they don't understand the result.

This error doesn't produce useful results if you Google the whole thing.

In this situation, students should identify which part of the error is the most important. In this case the phrase `could not find function "ggplot"` was the most important. Googling this part produces much more useful results.

In summary, the following skills help students to Google error messages effectively:

1. Write one line at a time, and test whether the code ran, and produced what the students expect
2. If students encounter an error...
3. Read the last thing they did to check it was what they intended
4. Read the error to check if they are familiar with it, or if it reveals typos


Does it contain one of these common error messages ?
* 'No such file or directory'
R cannot find the file, this could be because it is looking in the wrong place or you have mis-typed.[expand]
* 'Error: object 'name' not found'
R cannot find the object x. This could be because you've mistyped or because you need quotes around the name. [expand]
* 'Could not find function "name"'
R cannot find the function. This could be because you've mistyped or because you haven't used library() to load the package containing that function. [expand]

5. If you can't find anything you can understand, google the whole error message.

From the google search results click on the first item that contains stackoverflow this is the most useful site that coders use to ask and answer questions. If you don't understand the first answer you read don't worry it happens to all of us. Look at other stackoverflow questions and answers from the google search.


